Simulation study

### 2019-09-30 SPsim.Rmd
Simulate one example dataset

```{r setup}
source('R/SPreg.R', echo=FALSE)

@@

@@

```{r SimSetup}
sim.sp <- function(n, clustersize.gen, backbone.gen, 
                   covariate.gen, beta, link="cloglog"){

@@

   cs <- clustersize.gen(n)
   K <- max(cs)
   cov.mat <- covariate.gen(n)

@@

   th <- sapply(0:R, function(k)theta^k)
   lambda <- apply(th, 1, function(t)t * lambda0)
   rownames(lambda) <- 0:R

   q <- lapply(1:n,
               function(idx)p_from_lambda(lambda[,idx], n=cs[idx]))
   nresp <- lapply(q, function(qq)sample(seq_along(qq)-1, 
                                         size=1, prob=qq))
   res <- data.frame(ID=1:n,
                     ClusterSize = cs,
                     NResp = nresp)
   res <- cbind(res, cov.mat)
   res
}

@@

>>>>

```{r setup}
source('R/SPreg.R', echo=FALSE)
library(ggplot2)
theme_set(theme_classic())
```

@@

### Covariate-generating functions

Returns model matrix with randomly generated covariates

```{r Covgen}
cov.trt <- function(n, ntrts=4){
  obs <- rep(LETTERS[1:ntrts], length = n)
  dat <- data.frame(Trt = obs)
  dat
}

cov.bin_norm <- function(n, p=0.5){
  bin <- rbinom(n, size=1, prob=p)
  norm <- rnorm(n)
  data.frame(X1 = bin, X2 = norm)
}
```

@@

```{r SimSetup}
sim.sp <- function(n, clustersize.gen, backbone.gen, 
                   covariate.gen, formula, beta, link="log"){

@@

   cs <- clustersize.gen(n)
   K <- max(cs)
   covs <- covariate.gen(n)
   cov.mat <- model.matrix(formula, data=covs)

@@

   th <- sapply(0:K, function(k)theta^k)
   lambda <- apply(th, 1, function(t)t * lambda0)
   rownames(lambda) <- 0:K

   q <- lapply(1:n,
               function(idx)p_from_lambda(lambda[,idx], n=cs[idx]))
   nresp <- sapply(q, function(qq)sample(seq_along(qq)-1, 
                                         size=1, prob=qq))
   res <- data.frame(ID=1:n,
                     ClusterSize = cs,
                     NResp = nresp)
   res <- cbind(res, covs)
   res
}

@@

### Example of simulated data

```{r SimEx}
simd <- sim.sp(n = 100,
               clustersize.gen = cs.varied,
               backbone.gen = function(n)qpower.pdf(p=0.8, rho=0.5, n=n),
               covariate.gen = cov.trt,
               formula = ~Trt,
               beta = c(0, -0.5, -1, -2),
               link = "log")

ggplot(simd, aes(x=Trt, y=NResp/ClusterSize, size=ClusterSize)) +
  geom_jitter(width=0.1, height=0, alpha=0.5) +
  scale_size_area(breaks=c(1,5,10))
```

### Export multiple simulated sets

The GEE and beta-binomial models with log-links will be fitted in SAS.
